No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-20 R/MSE-manuscript.Rmd
Edit map to produce greyscale image; edit header levels.

# Get map background for plotting the map
world <- borders("world", colour="gray50", fill="gray50", alpha=0.75) # create a layer of borders
```

@@

# plot MSEs on map
MSE.map<-ggplot(data=map.data,aes(x=Longitude, y=Latitude,color=Drivers)) + world +
  geom_point(size=2.5) + geom_point(size = 2.5, colour = "grey", shape = 1) +
  scale_color_manual(values=c("#66CCCC","#006666"))+theme_void() +
  theme(legend.position = c(0.15, 0.25))

@@

# Results 
### What questions and management objectives do MSEs address? 
We found that uncertainty was the main driver of the system state included in management strategy evaluations, with uncertainty included in 21 of the 30 evaluations we reviewed in our random sample (Table \@ref(tab:drivers)).  In addition to uncertainty about the system model itself, monitoring methodology, how and what data is collected, was the most prevalent driver in MSE models, but a variety of drivers were considered across the random sample of MSEs.

@@

### Who is involved in MSEs? 
MSEs were rarely explicit about the roles participants played in MSE processes, as only one MSE documented the roles participants played in the process (Table \@ref(tab:roles)).  None of the MSEs noted whether or not public meetings were held in which the public was invited to participate.

@@

### Explore and expand upon this review
To aid learning from the documentation that has occurred, and provide ready access to future MSE documentation we produced a shiny application [@R-Shiny] to enable an interactive means to explore the MSE literature (<https://jonathancummings.shinyapps.io/MSEreview/>). The MSE review shiny application enables users to interactively explore the results presented in this article. The application includes additional analyses that may be of interest, such as an analysis of what journals MSEs have been published in, who is authoring MSEs, and more. Users may also filter by driver, location, species, or other characteristics of MSEs to explore a set of MSEs of interest and relevance to aid learning in the MSE practitioner community. We hope that as MSE are conducted they are entered here so that MSE practitioners can further learn from each other in the future.

>>>>

# Get map background for plotting the map
world <- borders("world", colour="gray85", fill="gray96", alpha=0.75) # create a layer of borders
```

@@

# plot MSEs on map
MSE.map<-ggplot(data=map.data,aes(x=Longitude, y=Latitude,color=Drivers)) + world +
  geom_point(size=2.5) + geom_point(size = 2.5, colour = "gray55", shape = 1) +
  scale_color_manual(values=c("gray10","gray55"))+theme_void() +
  theme(legend.position = c(0.15, 0.25))

@@

# Results 
## What questions and management objectives do MSEs address? 
We found that uncertainty was the main driver of the system state included in management strategy evaluations, with uncertainty included in 21 of the 30 evaluations we reviewed in our random sample (Table \@ref(tab:drivers)).  In addition to uncertainty about the system model itself, monitoring methodology, how and what data is collected, was the most prevalent driver in MSE models, but a variety of drivers were considered across the random sample of MSEs.

@@

## Who is involved in MSEs? 
MSEs were rarely explicit about the roles participants played in MSE processes, as only one MSE documented the roles participants played in the process (Table \@ref(tab:roles)).  None of the MSEs noted whether or not public meetings were held in which the public was invited to participate.

@@

## Explore and expand upon this review
To aid learning from the documentation that has occurred, and provide ready access to future MSE documentation we produced a shiny application [@R-Shiny] to enable an interactive means to explore the MSE literature (<https://jonathancummings.shinyapps.io/MSEreview/>). The MSE review shiny application enables users to interactively explore the results presented in this article. The application includes additional analyses that may be of interest, such as an analysis of what journals MSEs have been published in, who is authoring MSEs, and more. Users may also filter by driver, location, species, or other characteristics of MSEs to explore a set of MSEs of interest and relevance to aid learning in the MSE practitioner community. We hope that as MSE are conducted they are entered here so that MSE practitioners can further learn from each other in the future.
